---
title: "Introduction to 'pokemaster'"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{pokemaster}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(pokemaster)
```


## Overview of Functions

Our package has 4 main functions. 

- The first function is **pokedex**. It is a function that creates dataframe with features like id, name, stats, type. The default output of the function is a dataframe of all pokemons.

- The second function is **pokegen**. It takes an input of a vector of positive integer from 1 to 6. Example:  pokegen(3), and generate that number of pokemons. 

- The third function is **pokecard**, which generates a flashcard of the team. It takes the input of vector of up to 6 Pokemons and has an output of an image. 

- The forth function is **pokestats**. It is a function that plots barplot of the basic stats for each pokemon_data. It take an input vector of up to 6 pokemons, and generates an output ggbarplot. We provide visualization for hitpoints, attack, defense, sp attack, special defense, speed.

## Example 1 Pokemon Stats Comparison

The first example illustrates how our package can answer a question like 

- "How is Pikachu's stats compared with Eevee?"

This can be best answered by the **pokedex** function so we have see the stats of the two Pokemons, as well as the **pokestats** function because it nicely provides visualization of the key stats of the Pokemons.

```{r}
pokedex(c("pikachu", "eevee"))
```

Through this dataframe, we can directly compare the above two Pokemons on the key stats such as weight, height, base_experience, hp, attack, defense, special_attack, special_defense, speed, and their types.

```{r}
pokestats(myteam = c("pikachu","eevee"), "Pikachu v.s. Eevee")
```

According to the above visualization, Eevee has a higher hp, about the same attack, higher defense, less special attack, more special defense, and much less speed than Pikachu. 

## Example 2 Pokecard Generation

The second example illustrates how our package can answer a question like 

- "I am a Pokemon enthusiast. How can I generate a few postcards for my favorite pokemon team: pikachu, eevee, charizard, snorlax, ditto, and piplup. I want a postcard for the first three, the second three, and one for the whole team."

This can be best answered by the **pokecard** function because it generates a flashcard of the selected Pokemon. 

```{r}
pokecard(myteam = c("pikachu", "eevee", "charizard"), 
         color="LightBlue", title="Pikachu, Eevee, Charizard")
```
```{r}
pokecard(myteam = c("snorlax", "ditto", "venusaur"), 
         color="LightBlue", title="Snorlax, Ditto, Venusaur")
```

```{r}
pokecard(myteam = 
           c("pikachu","eevee", "charizard", "snorlax", "ditto", "venusaur"), 
              color="LightBlue", title="Whole Team")
```

Through the above code, we can help this Pokemon fan create their favorite postcard!!

## Example 3 Team Stat Comparison

The third example illustrates how our package can answer a question like 

- "I want to see how my favorite Pokemon team A: pikachu, eevee, charizard, snorlax, ditto, and piplup compare to another team B, which is composed of squirtle, mew, bulbasaur, lopunny, gible, and psyduck."

This question can be answered by showing the stats, creating the postcard to see how the teams are different visually, and by the comparing their stats in a bar plot.

```{r}
pokedex(c("pikachu","eevee", "charizard", "snorlax", "ditto", "venusaur"))
```

```{r}
pokedex(c("squirtle","mew", "bulbasaur", "rattata", "pidgey", "psyduck"))
```

From the above two tables, we can compare and contrast the specific stat that the pokemon fan is interested in within the two teams and across the teams.

```{r}
pokecard(myteam = 
           c("pikachu","eevee", "charizard", "snorlax", "ditto", "venusaur"), 
              color="LightBlue", title="Team 1")
```
```{r}
pokecard(myteam = 
           c("squirtle","mew", "bulbasaur", "rattata", "pidgey", "psyduck"), 
              color="LightBlue", title="Team 2")
```

We also generated beautiful graphics for the two teams.

```{r}
pokestats(myteam = c("pikachu","eevee", "charizard", "snorlax", "ditto", "venusaur"),
          "Team 1")
```

```{r}
pokestats(myteam = c("squirtle","mew", "bulbasaur", "rattata", "pidgey", "psyduck"),
          "Team 2")
```

From the above two bar plots, we can see how each of the Pokemons in each team can have varying capacities in different stats. From the above analysis, we cannot conclude that any of the team has much higher stats than the other. 

