---
title: "Introduction to 'Pokemaster'"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{pokemaster}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(pokemaster)
```

## Overview of Functions

Our package has 4 main functions. 

The first function is *POKEDEX*. It is a function that creates dataframe with features like id, name, stats, type. The output of the function is a dataframe of all pokemons.

The second function is *POKEGEN*. It takes an input of a vector of positive integer from 1 to 6. Example:  pokegen(3).

# 2. POKETEAM: flashcard of the team
# input: vector of up to 6 pokemons
# output: image
#
# 3. POKESTATS: function that plots barplot of the basic stats for each pokemon_data
# input: vector of up to 6 pokemons
# output: ggbarplot
# hitpoints, attack, defense, sp attack, special defense, speed

# 4. POKEFILTER: function that ranks and filters ALL pokemon based on different criteria (stats, type, etc)
# input: filter arguments
# output: filtered dataframe

# 5. team_generator (number of pokemons (6))
# output: vector of n random pokemons (#pikachu, "sd", "as", "asds")

## Example 1: 

A 600 - 1000 word vignette with at least 3 examples that showcase the questions you can answer with
the provided dataset and functions

```{r}
pokestats(myteam = c("pikachu","staryu"), "Best Team")
```



